\section{Professional Experience}
\textbf{Lead Engineer and Designer at \href{http://pauseandshine.com/}{Pause \& Shine} \hfill \small April 2013 - June 2013} 
\vspace{0.1cm}
\begin{innerlist}
\item Taught myself web design: typography, colors and layout. 
\item Used that knowledge to design and build the website, blog and marketing campaigns.
\item Built and designed in 9 days a mobile optimized meditation app with reminders and audio.
\end{innerlist}

\vspace{0.2cm}
\hspace{0.25cm}\textbf{\textit{Technologies}}: 
CSS3, HTML5, nodejs, backbonejs, mongodb

\vspace{0.4cm}

\textbf{Co-founder of \href{http://baytbaytak.com}{Baytbaytak} (Trulia of the middle east) \hfill \small Sep 2012 - March 2013} 
\vspace{0.1cm}
\begin{innerlist}
\item Built a platform that helped people search for appartments on a map-based website.  
\item Setup analytics to track customer behavior. This increased our conversion rates. 
\item Responsible for testing and deploying the app, and involved in strategic decisions.
\end{innerlist}

\vspace{0.2cm}
\hspace{0.25cm}\textbf{\textit{Technologies}}: 
nodejs, backbonejs, mongodb, gMaps API, Google Analytics, Mixpanel

\vspace{0.4cm}

\textbf{
  Software Engineer at \href{http://anghami.com/}{Anghami}, (Spotify of the middle east)
  \hfill \small June 2012 - August 2012
}
\vspace{0.1cm}
\begin{innerlist}
\item Researched state of the art techniques in recommendation systems.
\item Tested available recommendation system technologies (Hadoop, Google compute engine)
\item Built a recommender system using lastfm's API.
\end{innerlist}


\vspace{0.2cm}
\hspace{0.25cm}\textbf{\textit{Technologies}}: 
nodejs, mongodb, lastfm API, REST API's

\vspace{0.4cm}

\textbf{Summer Scholar at \href{http://www.ri.cmu.edu/}{Carnegie Mellon University, Robotics Institute}}
\hfill \textbf{Summer 2011}
\vspace{0.1cm}

Google Core AI Project, a \textit{predictive indoor Navigation application}.

\vspace{0.1cm}
\begin{innerlist}
\item Made the product available to mobile consumers by porting the technology to Android.
\item Created a server-side prediction module that reduced the computational load on the client by 30x.
\end{innerlist}

\vspace{0.2cm}
\hspace{0.25cm}\textbf{\textit{Technologies}}: 
Java, android, HMM, MDP

%\vspace{0.6cm}

%\textbf{\href{http://webfea.fea.aub.edu.lb/itunit/home.aspx}{\textbf{ IT unit}} assisant at AUB's Faculty of Engineering and Architecture} 
%\begin{outerlist}
%\item[] \textit{I provided IT support to faculty, staff, and graduate students}
%        \hfill \small Fall 2008 - Spring 2010 \normalsize
%\end{outerlist}
